\documentclass[a4paper]{article}
%\usepackage{simplemargins}

%\usepackage[square]{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}

\begin{document}
\pagenumbering{gobble}

\Large
 \begin{center}
Application for Bike Sharing\\ 
Risk assessment

\hspace{10pt}

% Author names and affiliations
\large
Cristian Hasna$^1$ \\
Marțincu Petru$^1$ \\
Mircea Rareș - Gabriel$^1$ \\

\hspace{10pt}

\small  
$^1$ Faculty of Computer Science, ”Alexandru Ioan Cuza” University, Graduate Student\\ 

\end{center}

\hspace{10pt}

\textbf{Risk event} \ \\

\normalsize

\ \\
\textbf{1. Stolen bike}
\begin{itemize}
\item Timeframe: Anytime
\item Probability: Crime rate for the current city.
\item Impact: Number of available bikes decreases.
\item Factors: Weak security such as no locker or a weak type of locker.
\end{itemize}
\ \\ \ \\ 
\textbf{2. Too many idle bikes}
\begin{itemize}
\item Timeframe: Anytime
\item Probability: Medium - High
\item Impact: Too many bikes are left unused, deeming them costly to run.
\item Factors: No study is being made before launching the app in the specific city, thus having a low demand and a great supply will only rise the number of idle bikes.
\end{itemize}
\ \\ \ \\ 
\textbf{3. Waiting time for a bike is big}
\begin{itemize}
\item Timeframe: Anytime 
\item Probability: Medium - High
\item Impact: Very few bikes have been bought, waiting time for a bike will rise sharply when the demand is big.
\item Factors: Few bikes have been bought in a city where the demand is high, thus creating a situation of high demand - low supply.
\end{itemize}
\ \\ \ \\ 
\textbf{4. Users are holding on to the bikes}
\begin{itemize}
\item Timeframe: Anytime 
\item Probability: Low - Medium 
\item Impact: Number of available bikes decreases. Some users will go and claim that bike, but won't have access to it, given the fact that their access is blocked.
\item Factors: Some users hide the bikes in the appartment blocks where the GPS signal is weak, and other users are obstructed.
\end{itemize}
\ \\ \ \\ 
\textbf{5. Defect bikes}
\begin{itemize}
\item Timeframe: Anytime 
\item Probability: Low - Medium
\item Impact: Bike becomes unusuable. Money has to be spent to fix it.
\item Factors: Gradual degradation to the bikes, because of little to none maintenance. Some users might abuse them and wreck them, rendering the bikes unusuable. Force majeure.
\end{itemize}
\ \\ \ \\ 

\end{document}
